Toxic Code Snippets on Stack Overflow

### 2018-06-20 cloverflow-tse/cover_letter/cover_letter.tex
Added the separated Abstract PDF (required by TSE) and updated the Novelty Statement + small fixes in the cover letter.

Lastly, we would also like to ask the reviewers to comment on how to address the
newly established page limits of IEEE TSE that was enforced on 18 February 2018, after our previous
submission (15 November 2017). After incorporating the suggestions from the reviewers and
rewriting, our paper is now extended to 22 pages. Are there any elements that
could or should be removed, or should a split into two separate papers be
considered?

@@

	\item To address your point about auditing platforms/services, we performed a
	study of two open source software auditing platforms/services:~BlackDuck
	Software\footnote{https://www.blackducksoftware.com} and
	nexB\footnote{https://www.nexb.com}. For BlackDuck Software, we found from
	their report~\cite{CORSI2017} that while they check for code copied from open
	source projects including GitHub and Stack Overflow and analyse their license
	compatibility with their customer software, the BlackDuck auditing system will
	treat the code snippets on Stack Overflow as having an ``unknown'' license because
	it does not know the original license of Stack Overflow code snippets. For
	nexB, their product does not mention checking of reused source code from Stack
	Overflow. So, our proposed preventive measure, which can offer more precise
	licensing information of Stack Overflow code snippets, will be useful as an
	add-on license check for code copying from Stack Overflow. We include this in
	the Overall Discussion. \end{enumerate}

@@

\begin{enumerate} 
	\item For the Stack Overflow data set, the value represents
	the median size of Stack Overflow code snippets. For the Qualitas data set, the
	value represents the median of the number of lines of code in each project. Since
	they are confusing as you pointed out, we decided to remove them from the table
	and only discuss the numbers in the text. 
	\item This is a great insight! We expanded the idea further and came up with a suggestion for an
	automated technique to facilitate human investigator on finding provenance and
	included it in a section called Automated cloning direction detection in the
	Overall Discussion. 
	\item Thanks. This has been fixed. \end{enumerate}

>>>>

%Lastly, we would also like to ask the reviewers to comment on how to address the
%newly established page limits of IEEE TSE that was enforced on 18 February 2018, after our previous
%submission (15 November 2017). After incorporating the suggestions from the reviewers and
%rewriting, our paper is now extended to 22 pages. Are there any elements that
%could or should be removed, or should a split into two separate papers be
%considered?

@@

	\item To address your point about auditing platforms/services, we performed a
	study of two open source software auditing platforms/services:~BlackDuck
	Software\footnote{https://www.blackducksoftware.com} and
	nexB\footnote{https://www.nexb.com}. For BlackDuck Software, we found from
	their report~\citep{CORSI2017} that while they check for code copied from open
	source projects including GitHub and Stack Overflow and analyse their license
	compatibility with their customer software, the BlackDuck auditing system will
	treat the code snippets on Stack Overflow as having an ``unknown'' license because
	it does not know the original license of Stack Overflow code snippets. For
	nexB, their product does not mention checking of reused source code from Stack
	Overflow. So, our proposed preventive measure, which can offer more precise
	licensing information of Stack Overflow code snippets, will be useful as an
	add-on license check for code copying from Stack Overflow. We include this in
	the Overall Discussion. \end{enumerate}

@@

\begin{enumerate} 
	\item For the Stack Overflow data set, the value represents
	the median size of Stack Overflow code snippets. For the Qualitas data set, the
	value represents the median of the number of lines of code in each project. Since
	they are confusing as you pointed out, we decided to remove them from the table
	and only discuss the numbers in the text. 
	\item This is a great insight! We expanded the idea further and came up with a suggestion for an
	automated technique to facilitate human investigator on finding clone provenance and
	included it in a section called Automated cloning direction detection in the
	Overall Discussion. 
	\item Thanks. This has been fixed. \end{enumerate}
